---
title: "HW4"
output: html_document
date: "2022-11-12"
---

```{r message=FALSE}
library(tidyverse)
library(BSDA)
library(readxl)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE)
```

## Problem1

```{r}
blood_data = c(125, 123, 117, 123, 115, 112, 128, 118, 124, 111, 116, 109, 125, 120, 113, 123, 112, 118, 121, 118, 122, 115, 105, 118, 131)
blood_test_data = blood_data - 120
SIGN.test(blood_test_data, alternative = "less", conf.level = 0.95)
```

* a)
  According to the sign-test above, we can see that the test statistic is **what?** with p-value **0.2706**. Thus we fail to reject the null hypothesis under a 0.05 significant level and claim that the median blood sugar readings was 120 in the population from which the 25 patients were selected.
 
```{r}
wilcox.test(blood_test_data, alternative = "less", conf.level = 0.95)
``` 
* b)
  According to Wilcoxon signed-rank test, we can see that the test statistic is **what?** with p-value **0.1447**. Thus we fail to reject the null hypothesis under a 0.05 significant level and claim that the median blood sugar readings was 120 in the population from which the 25 patients were selected.
  
  
## Problem 2
```{r}
brain_data = 
  read_xlsx("./Brain.xlsx")[-c(1),] %>% 
  janitor::clean_names()

brain_fit = 
  lm(glia_neuron_ratio ~ ln_brain_mass, data = brain_data) 

brain_fit %>% 
  broom::tidy()
```
* a) 
  The linear model for the nonhuman data using ln (brain mass) as the predictor is : **y = 0.181x + 0.164**.

```{r}
y_0 = 0.181*7.22 + 0.164
```

* b)
  The predicted glia-neuron ratio for humans is **`r y_0`**.

* c)

* d)

* e)







